Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-05 WSSSPE1_report/WSSSPE1_summary_report.tex
adding leads and volunteers, also adding Katz NSF ack

Additional volunteers:
\begin{itemize}
\item Chris Mattmann $\langle$\url{chris.a.mattmann@jpl.nasa.gov}$\rangle$
\item * Ketan Maheshwari $\langle$\url{ketancmaheshwari@gmail.com}$\rangle$
\item Marlon Pierce $\langle$\url{marpierc@iu.edu}$\rangle$
\item Colin Venters $\langle$\url{C.Venters@hud.ac.uk}$\rangle$
\item Suresh Marru $\langle$\url{smarru@iu.edu}$\rangle$
\item Lynn Zentner $\langle$\url{lzentner@purdue.edu}$\rangle$
\item Anne Elster $\langle$\url{anne.elster@gmail.com}$\rangle$
\item Shel Swenson $\langle$\url{mdswenso@usc.edu}$\rangle$
\item Andy Ray Terrel $\langle$\url{andy.terrel@gmail.com}$\rangle$
\item Abani Patra $\langle$\url{abani.patra@gmail.com}$\rangle$
\item Nancy Wilkins-Diehr $\langle$\url{wilkinsn@sdsc.edu}$\rangle$
\item James Spencer $\langle$\url{j.spencer@imperial.ac.uk}$\rangle$
\item * Frank Löffler $\langle$\url{knarf@cct.lsu.edu}$\rangle$
\item * James Hetherington $\langle$\url{j.hetherington@ucl.ac.uk}$\rangle$
\item * Sou-Cheng (Terrya) Choi $\langle$\url{sou.cheng.terrya.choi@gmail.com}$\rangle$
\item James Howison $\langle$\url{james@howison.name}$\rangle$
\item * Bruce Berriman $\langle$\url{gbb@ipac.caltech.edu}$\rangle$
\item Hilmar Lapp $\langle$\url{hlapp@nescent.org}$\rangle$
\item * Marcus D. Hanwell $\langle$\url{marcus.hanwell@kitware.com}$\rangle$
\item Lucas Nussbaum $\langle$\url{lucas.nussbaum@loria.fr}$\rangle$
\item Matthew Turk $\langle$\url{matthewturk@gmail.com}$\rangle$
\end{itemize}

@@

@@

@@

@@

\item Frank Löffler, Steven R. Brandt, Gabrielle Allen and Erik
  Schnetter. Cactus: Issues for Sustainable Simulation Software
  \cite{Loffler_WSSSPE}

@@

@@

@@

@@

@@

\note{Dan: do we need this section?  I think there's some overlap
  between this and the discussion in the Developing and Support
  Software section.  Or perhaps this should go in the cross-cutting
  issues section?}

@@

@@

@@

\begin{tabular}{ L{4cm}  L{4cm}  L{4cm}  L{4cm} }
   Daniel S. Katz
&  Neil Chue Hong
&  Gabrielle Allen
&  David Proctor
\\ Manish Parashar
&  Jay Alameda
&  David Andrs
&  Lorena A Barba
\\ David Bernholdt
&  Phil Bourne
&  Karl Broman
&  Maxine Brown
\\ David Bruhwiler
&  Bruno Bzeznik
&  Jeffrey Carver
&  John W. Cobb
\\ Karen Cranston
&  Rion Dooley
&  Anshu Dubey
&  Ian Foster
\\Juliana Freire
& Derek Gaston
& Derek Groen
& Edmund Hart
\\James Hetherington
& Simon Hettrick
& Kenneth Hoste
& James Howison
\\Daisie Huang
& Kerk Kee
& Arnaud Legrand
& Paul Madden
\\Louis Maddox
& Ketan Maheshwari
& Suresh Marru
& Cezary Mazurek
\\James McClure
& Chris Mentzel
& J. Yates Monteith
& Pierre Neyron
\\Lucas Nussbaum
& Cody Permann
& John Peterson
& Quan Pham
\\Marlon Pierce
& Heather Piwowar
& Jason Riedy
& Andreas Schreiber
\\William Scullin
& Andrew Slaughter
& Arfon Smith
& James Spencer
\\Shel Swenson
& Fr\'{e}d\'{e}ric Suter
& Andy Terrel
& George  Thiruvathukal
\\John Towns
& Erik Trainer
& Matthew Turk
& Eric Van Wyk
\\Colin C. Venters
& Von Welch
& Nancy Wilkins-Diehr
& Theresa Windus
\\Rich Wolski
& Lynn Zentner
& Frank Löffler
& Patrick O'Leary
\end{tabular}

>>>>

Additional volunteers:
\begin{itemize}
\item Chris Mattmann $\langle$\url{chris.a.mattmann@jpl.nasa.gov}$\rangle$
\item * Ketan Maheshwari $\langle$\url{ketancmaheshwari@gmail.com}$\rangle$
\item Marlon Pierce $\langle$\url{marpierc@iu.edu}$\rangle$
\item Colin Venters $\langle$\url{C.Venters@hud.ac.uk}$\rangle$
\item Suresh Marru $\langle$\url{smarru@iu.edu}$\rangle$
\item Lynn Zentner $\langle$\url{lzentner@purdue.edu}$\rangle$
\item Anne Elster $\langle$\url{anne.elster@gmail.com}$\rangle$
\item Shel Swenson $\langle$\url{mdswenso@usc.edu}$\rangle$
\item Andy Ray Terrel $\langle$\url{andy.terrel@gmail.com}$\rangle$
\item Abani Patra $\langle$\url{abani.patra@gmail.com}$\rangle$
\item Nancy Wilkins-Diehr $\langle$\url{wilkinsn@sdsc.edu}$\rangle$
\item James Spencer $\langle$\url{j.spencer@imperial.ac.uk}$\rangle$
\item * Frank L\"{o}ffler $\langle$\url{knarf@cct.lsu.edu}$\rangle$
\item * James Hetherington $\langle$\url{j.hetherington@ucl.ac.uk}$\rangle$
\item * Sou-Cheng (Terrya) Choi $\langle$\url{sou.cheng.terrya.choi@gmail.com}$\rangle$
\item James Howison $\langle$\url{james@howison.name}$\rangle$
\item * Bruce Berriman $\langle$\url{gbb@ipac.caltech.edu}$\rangle$
\item Hilmar Lapp $\langle$\url{hlapp@nescent.org}$\rangle$
\item * Marcus D. Hanwell $\langle$\url{marcus.hanwell@kitware.com}$\rangle$
\item Lucas Nussbaum $\langle$\url{lucas.nussbaum@loria.fr}$\rangle$
\item Matthew Turk $\langle$\url{matthewturk@gmail.com}$\rangle$
\end{itemize}

@@

\note{lead: Sou-Cheng (Terrya) Choi}

@@

\note{lead: Marcus Hanwell, contributors: Suresh Marru}

@@

\note{lead: Colin Venters}

@@

\item Frank L\"{o}ffler, Steven R. Brandt, Gabrielle Allen and Erik
  Schnetter. Cactus: Issues for Sustainable Simulation Software
  \cite{Loffler_WSSSPE}

@@

\note{lead: Matthew Turk, contributors: Nancy Wilkins-Diehr, Chris Mattmann, Suresh Marru, Frank L\"{o}ffler, Andy Terrel}

@@

\note{all to put notes here of stuff that doesn't fit elsewhere, if any}

\todo{perhaps remove this section}

@@

\note{lead: Daniel S. Katz}

@@

\note{lead: Ketan Maheshwari, contributors: Andy Terrel}

@@

\note{Dan: do we need this section?  I think there's some overlap
  between this and the discussion in the Developing and Support
  Software section.  Or perhaps this should go in the cross-cutting
  issues section?  Let's write it down here - then we can decide if it goes elsewhere}

@@

\todo{anyone who needs to put something in here should}

Some of the work by Katz was
supported by the National Science Foundation while working at the
Foundation; any opinion, finding, and conclusions or recommendations
expressed in this material are those of the author(s) and do not
necessarily reflect the views of the National Science Foundation.

@@

\note{lead: Shel Swenson}

\note{should alphabetize all, but if we get more from the SC13 folks, it's not worth spending
time doing this now.  I wonder if there's a way to just have a simple list that we can keep ordered, and let LaTeX do the formatting, rather than manually creating a table as this is now}

@@

\begin{tabular}{ L{4cm}  L{4cm}  L{4cm}  L{4cm} }
   Daniel S. Katz
&  Neil Chue Hong
&  Gabrielle Allen
&  David Proctor
\\ Manish Parashar
&  Jay Alameda
&  David Andrs
&  Lorena A Barba
\\ David Bernholdt
&  Phil Bourne
&  Karl Broman
&  Maxine Brown
\\ David Bruhwiler
&  Bruno Bzeznik
&  Jeffrey Carver
&  John W. Cobb
\\ Karen Cranston
&  Rion Dooley
&  Anshu Dubey
&  Ian Foster
\\Juliana Freire
& Derek Gaston
& Derek Groen
& Edmund Hart
\\James Hetherington
& Simon Hettrick
& Kenneth Hoste
& James Howison
\\Daisie Huang
& Kerk Kee
& Arnaud Legrand
& Paul Madden
\\Louis Maddox
& Ketan Maheshwari
& Suresh Marru
& Cezary Mazurek
\\James McClure
& Chris Mentzel
& J. Yates Monteith
& Pierre Neyron
\\Lucas Nussbaum
& Cody Permann
& John Peterson
& Quan Pham
\\Marlon Pierce
& Heather Piwowar
& Jason Riedy
& Andreas Schreiber
\\William Scullin
& Andrew Slaughter
& Arfon Smith
& James Spencer
\\Shel Swenson
& Fr\'{e}d\'{e}ric Suter
& Andy Terrel
& George  Thiruvathukal
\\John Towns
& Erik Trainer
& Matthew Turk
& Eric Van Wyk
\\Colin C. Venters
& Von Welch
& Nancy Wilkins-Diehr
& Theresa Windus
\\Rich Wolski
& Lynn Zentner
& Frank L\"{o}ffler
& Patrick O'Leary
\end{tabular}
